\documentclass[11pt, letterpaper]{article}

% Harvard-style packages
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{tabularx}

% Font setup
\setmainfont{Times New Roman}[
  BoldFont = Times New Roman Bold,
  ItalicFont = Times New Roman Italic
]

% Color scheme
\definecolor{harvardcrimson}{RGB}{165, 28, 48}
\definecolor{darkgray}{RGB}{64, 64, 64}
\definecolor{lightgray}{RGB}{128, 128, 128}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=harvardcrimson,
    filecolor=harvardcrimson,
    urlcolor=harvardcrimson,
    citecolor=harvardcrimson
}

% Section formatting
\titleformat{\section}
  {\Large\bfseries\color{harvardcrimson}}
  {}
  {0pt}
  {}
  [\vspace{2pt}\titlerule\vspace{8pt}]

\titleformat{\subsection}
  {\large\bfseries\color{darkgray}}
  {}
  {0pt}
  {}
  [\vspace{4pt}]

% Custom commands
\newcommand{\name}[1]{\centerline{\Huge\bfseries\color{harvardcrimson}#1}}
\newcommand{\contact}[1]{\centerline{\large\color{darkgray}#1}}
\newcommand{\position}[3]{
  \textbf{#1} \hfill \textit{#2} \\
  #3 \vspace{6pt}
}
\newcommand{\education}[4]{
  \textbf{#1} \hfill \textit{#2} \\
  #3 \\
  #4 \vspace{6pt}
}

% Spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\raggedbottom

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\name{Tinotenda Musikavanhu}
\vspace{12pt}
\contact{Frontend Engineer \textbullet\ AI Integration \textbullet\ Systems Design}
\vspace{8pt}
\contact{
  \faIcon{envelope} \href{mailto:tinotenda@safehavelabs.org}{tinotenda@safehavelabs.org} \textbullet\
  \faIcon{phone} 231-260-6380 \textbullet\
  \faIcon{map-marker-alt} Abilene, TX
}
\vspace{4pt}
\contact{
  \faIcon{globe} \href{https://tinomusika.netlify.app}{Portfolio} \textbullet\
  \faIcon{linkedin} \href{https://www.linkedin.com/in/tino-m-630086124}{LinkedIn} \textbullet\
  \faIcon{github} \href{https://github.com/Musikavanhu}{GitHub}
}

\vspace{20pt}

% ── Summary ─────────────────────────────────────────────────────────────────
\section{Professional Summary}
My full name is Tinotenda Musikavanhu, but professionally, I prefer to be addressed as Tino. My passion for software development emerged when I aspired to establish my own business. In this endeavor, I learned how to develop iOS applications and collaborated with a team of skilled professionals, including a senior engineer. This experience served as my initial exposure to the tech industry and sparked my curiosity to explore further. Over time, I immersed myself in multiple programming languages, and I was fortunate enough to share my knowledge with a vast audience of over 30,000 followers on social media platforms. What began as simple projects utilizing online resources transformed into personally gratifying work, and I even ventured into the realm of tutoring.

Overall, my journey into software development has been one of self-discovery, learning, and growth. I am confident that my experience, coupled with my passion for technology, has provided me with a solid foundation to excel in this field.

\vspace{8pt}

% ── Education ───────────────────────────────────────────────────────────────
\section{Education}

\education{Southern Methodist University}{2016 -- 2020}{Computer Science}{
  \textit{Emphasis:} Systems Engineering \& Artificial Intelligence \\
  \textit{Location:} Dallas, TX
}

\education{Harvard University Extension School}{Ongoing}{Bachelor of Arts - Computer science}{
  An intensive and comprehensive course covering a wide range of computer science topics. Acquired expertise in multiple programming languages, including JavaScript , Sql , and C++, and gained hands-on experience in software development, algorithms, data structures, and artificial intelligence. Developed strong analytical and problem-solving skills, enabling the ability to analyze complex problems and develop effective solutions. Participated in collaborative projects and worked with diverse teams, fostering excellent communication and teamwork abilities. Completed the program with a solid understanding of computer science principles and practices, ready to apply this knowledge to real-world challenges.
}

% ── Professional Experience ──────────────────────────────────────────────────
\section{Professional Experience}

\position{Software Engineer}{}{
  \textbf{Safehaven}
  \begin{itemize}[leftmargin=20pt, itemsep=2pt]
    \item Develop, maintain, and enhance Safehaven's software products using JavaScript and other relevant technologies.
    \item Collaborated with cross-functional teams including designers, product managers, and other developers to implement new features and functionality.
    \item Wrote clean, efficient, and maintainable code that adheres to industry standards and best practices.
    \item Conducted code reviews and provide constructive feedback to other team members to ensure high-quality codebase.
    \item Ensure that software products are tested thoroughly and perform optimally across various platforms and browsers.
    \item Stayed up-to-date with the latest trends and advancements in JavaScript and related technologies, and incorporate them into the product development process.
    \item Participated in the development of technical documentation, user manuals, and other related materials.
    \item Troubleshoot and resolve technical issues reported by users, and provide timely support as needed.
  \end{itemize}
}

\position{Software Engineer}{}{
  \textbf{Protatech}
  \begin{itemize}[leftmargin=20pt, itemsep=2pt]
    \item Experienced Database Analyst and Developer with a proven track record of designing, developing, and maintaining complex databases for various applications. Adept at working collaboratively with cross-functional teams to understand business requirements and ensuring that database solutions meet those requirements. Possesses a strong ability to analyze and forecast potential database concerns, developing effective solutions and streamlining processes. Exceptional communication skills and proficiency in multiple programming languages including Angular, SQL, and Swift. Demonstrated success in enhancing client response time and delivering products ahead of schedule.
    \item Analyzed and Foretasted Database concerns for the NFL’s Employee management database on site at the Super Bowl. Executed more than 5,000 employee verifications, which Streamlined to 15\% of all attendance to be assigned perfectly.
    \item Supported a new enterprise application in the Angular framework for risk management. Redesigned 75\% of the existing database structure; Later shaped the product delivery to be assigned to the client two days earlier.
    \item Streamlined current bugs of employee management application directly with clients. Client response time and remedy now enhanced to be 20\% faster with new hours of operation.
  \end{itemize}
}

% ── Technical Skills ─────────────────────────────────────────────────────────
\section{Technical Skills}

\begin{multicols}{2}
\textbf{Frontend \& Web}
\begin{itemize}[leftmargin=15pt, itemsep=1pt]
  \item React, Next.js, TypeScript
  \item Framer Motion, Tailwind CSS
  \item Responsive Design, Web Perf
  \item Vanilla CSS, HTML5, SVG
\end{itemize}

\textbf{AI \& Machine Learning}
\begin{itemize}[leftmargin=15pt, itemsep=1pt]
  \item PyTorch, HuggingFace Transformers
  \item Latent Space \& Diffusion Models
  \item LLM Integration (LM Studio, OpenAI)
  \item Reinforcement Learning
\end{itemize}

\textbf{Backend \& Systems}
\begin{itemize}[leftmargin=15pt, itemsep=1pt]
  \item Node.js, REST APIs, WebSockets
  \item Distributed Systems Architecture
  \item Real-time Data Pipelines
  \item Cyber-Physical Resilience
\end{itemize}

\textbf{Tools \& Platforms}
\begin{itemize}[leftmargin=15pt, itemsep=1pt]
  \item Git, GitHub, Vercel, Netlify
  \item Apple MPS / GPU Training
  \item Figma, System Design
  \item Zenodo Open Science
\end{itemize}
\end{multicols}

% ── Selected Projects ─────────────────────────────────────────────────────────
\section{Selected Projects}

\textbf{AI Gameplay Automation System (Sims~4)} \hfill \textit{Python, React, Computer Vision} \\
Autonomous AI agent that plays and manages a Sims~4 household using computer vision, decision trees, and reinforcement learning. Features a real-time React monitoring dashboard with live game-state telemetry. \\[4pt]

\textbf{GenesisTrader} \hfill \textit{Next.js, TypeScript, Coinbase API} \\
AI-powered cryptocurrency trading system with predictive analytics, real-time market intelligence, and a high-performance Next.js frontend. Integrates local LLM reasoning for trade signal generation. \\[4pt]

\textbf{AI Systems Research --- Latent Planning + Autoregressive Gen} \hfill \textit{PyTorch, HuggingFace, MPS} \\
Independent research training custom transformer architectures to explore latent planning as a mechanism for improved autoregressive text and image generation quality. \\[4pt]


% ── Selected Publications ─────────────────────────────────────────────────────
\section{Selected Publications}
\textit{Full list available at: \href{https://zenodo.org/search?q=Musikavanhu}{zenodo.org/Musikavanhu}}

\begin{itemize}[leftmargin=20pt, itemsep=4pt]
  \item \textbf{Musikavanhu, T.} (2025). ``SolarTherm-CarbCap (STCC): Integrated Solar-Thermal Carbon Capture for Climate Remediation.'' \href{https://zenodo.org/records/15711985}{DOI: 10.5281/zenodo.15711985}
  \item \textbf{Musikavanhu, T.} (2025). ``Thermodynamic Validation of Anthropogenic Climate Acceleration'' \href{https://zenodo.org/records/16422926}{DOI: 10.5281/zenodo.16422926}
  \item \textbf{Musikavanhu, T.} (2025). ``Quantum Zeta Field Theory: Unifying Framework for Quantum Fields and Mathematical Structures.''
\end{itemize}

% ── Awards ────────────────────────────────────────────────────────────────────
\section{Awards \& Recognition}

\begin{itemize}[leftmargin=20pt, itemsep=3pt]
  \item \textbf{Open Science Impact} (2024--2025): 500+ research downloads across 64+ publications on Zenodo
  \item \textbf{NASA Recognition} (2025): Acknowledged by former NASA Administrator Dan Goldin for research contributions
  \item \textbf{High-Stakes Ops} (2019--2025): Zero-downtime delivery for Super Bowl-scale event deployments at ProtaTECH
\end{itemize}

\vspace{16pt}
\centerline{\textit{``Building the future --- one component, one model, one breakthrough at a time.''}}

\end{document}
